\section{Systems and subsystems}
For our bike manufacturing company, we have defined 3 primary systems that will be discussed in this section. These systems should be sufficient to accept an order, manage the supply of all materials, and manage the whole production line.

\subsection{Enterprise resource system}
First to mention is an enterprise resource system whose first step is to receive orders. After an order is received the system generates an invoice for the customer and tries to predict the time needed to complete the bike. This estimate is based on other subsystems such as the production capacity system or human resource planning system. In case of unhappy customers, this system also handles customer support including accepting the complaint and assigning it to employees.

\subsection{Suply chain management system}
This system is used to manage the supply chain and logistics. Part of the logistics is ensuring that there is enough material in the warehouses -- this is managed by an inventory subsystem. If there are materials missing and need to be ordered that's when the procurement subsystem comes in handy. This subsystem consists of a blockchain of vendors and a tracking system which helps us with planning. Since we consider collecting data from various suppliers there is also a quality history system helping with decision-making when it comes to choosing a supplier.

\subsection{Production management system}
This is the system where the actual production of a bike takes place. Apart from the production itself, also a scheduling system is a must, in order to achieve maximal efficiency. Another mentionable subsystem is quality control where it is ensured that every bike meets industry standards. It is inevitable that there might occur some errors in the production line and therefore there is also an existence of an error handling system ensuring fault correction and recovery. Integration of some bike components can´t be assembled fully by robots and that is when assembly technicians come in. That creates a need for safety requirements ensuring no human is harmed. That is a responsibility of a security system.