\documentclass{article}

\title{}
\date{}

\begin{document}

\maketitle

\section{Use Cases}
Name: Introduction of a new bike model \\
Actors: Assembly technician, production manager, production scheduler \\
Preconditions: A design of the new bike, specifying the required production steps and what machines are required, exists.

Steps:
\begin{enumerate}
\item The production manager logs into the the production software.
\item The production manager configures a new production step in the software.

\item The production manager asks the assembly technician to add new hardware to the assembly line.

\item The assembly technician installs hardware to the assembly line.

\item The production manager configures a new production run including the new production step in the software.

\item The production manager schedules a test run.

\item The production scheduler confirms the test schedule and starts the production run.
\item The assembly technician and production manager confirm the correctness of the newly established production run.


\end{enumerate}

Postconditions: A new bike resembling a test artifact of the newly established production run. \\


Name: Emergency shutdown due to malfunctioning test bench \\
Actors: Test bench, quality assurance worker \\
Preconditions: QA Worker performs quality assurance of the produced bike at a test bench. The test bench includes the use of robotic arms for easier inspection of the bike.
\begin{enumerate}
    \item The quality assurance worker starts his inspection of the produced bike. Therefore, he uses a test bench that utilizes robotic arms enabling easier inspection of the bike (i.e. the robotic arms help to lift, rotate, etc. the bike).
    \item While standing very close to the bike, the robotic arms begin to move the bike in unpredictable ways.
    \item Sensors detect the proximity of the human worker to the malfunctioning machine.
    \item The security system interprets it as threat to the human worker.
    \item The security system shuts the malfunctioning test bench down and reports the shutdown to the supervisory system.
\\

\end{enumerate}

Postconditions: The production machine is shutdown and remaining work is load-balanced to the other machines that are available.




\end{document}
